Clustering/Orthofinder analysis

### 2022-01-16 analysis/Orthofinder.Rmd
Add missing files
better analysis

@@

>>>>

Here I use Orthofinder results to pull out genes unique to seagrasses, unique to duckweeds, and make some nice summary tables

@@

# FINAL version redoing - terrestrial vs aquatics vs seagrasses

Plotting all species separately is messy as I have so many species. I'm joining the species into three groups: aquatics, terrestrials, and seagrasses!

```{r}
per_group_spec <-
  per_spec %>% mutate(group = case_when(
    name %in% c(
      'A. trichopada',
      'B. distachyon',
      'O. sativa',
      'P. patens',
      'P. trichocarpa',
      'S. moellendorffii',
      'A. thaliana',
      'T. parvula',
      'V. vinifera',
      'Z. mays'
    ) ~ 'Terrestrial',
    name %in% c(
      'C. reinhardtii',
      'L. gibba',
      'S. polyrhiza',
      'O. lucimarinus',
      'W. australis'
    ) ~ 'Aquatic',
    name %in% c('P. australis', 'Z. muelleri', 'Z. marina', 'A. antarctica') ~ 'Seagrasses'
  )) 
```

```{r}
# now I want the data in this format:
# listInput <- list(one = c(1, 2, 3, 5, 7, 8, 11, 12, 13), two = c(1, 2, 4, 5, 
#   10), three = c(1, 5, 6, 7, 8, 9, 10, 12, 13))
groupx <- per_group_spec %>% 
  select(group, Orthogroup) %>% # turn the table around
  deframe() # convert to named vector
```

```{r}
mylistgroup <- lapply(split(groupx, names(groupx)), unname) # yuck - ugly code to convert the named vector to a list
```

```{r}
xgroup <- upset(fromList(mylistgroup), order.by='freq', nsets = length(groups) - 1)
```

```{r fig.width=10}
xgroup
```

MUCH better. The biggest chunk of orthogroups is not in aquatics or seagrasses with 13562 orthogroups. 3437 orthogroups are unique to aquatics, but not in seagrasses - 1183 orthogroups are unique in seagrasses, but not in aquatics. 404 + 3437 + 2217 orthogroups are not in terrestrials.
